Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-01 paper/paper-nature-revised.tex
paper revisions

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{April 27, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi

@@

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Finally, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned.

@@

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, questions were incorrectly transcribed under
an answer node and vice-versa, in which cases we manually corrected the
question and answer flags. For instance, we check for any statements
flagged as questions which include the phrase ``has provided the
following answer to the honourable member's question'', in which case we
re-code that statement as an answer.

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.

@@

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022, so there are 1,517 files for each format. All data
records are available on the general-purpose repository Zenodo, at
https://doi.org/10.5281/zenodo.7336075 (Katz and Alexander 2023). For
each file, each row contains an individual statement, with details on
the individual speaking. For general statements transcribed as made by
``Honourable members'' for example, these variables cannot be specified.
Table~\ref{tbl-vars} provides an overview of each variable found in the
database.

@@

\centering
\begin{tabular}{ll}
\toprule
Variable & Description\\
\midrule
name & Name of speaker\\
order & Row number\\
speech\_no & Speech number\\
page.no & Page number statement can be found on in official Hansard\\
time.stamp & Time of statement\\
\addlinespace
name.id & Unique member identification code, based on the Parliamentary Handbook\\
electorate & Speaking member's electorate\\
party & Speaking member's party\\
in.gov & Flag for in government (1 if in government, 0 otherwise)\\
first.speech & Flag for first speech (1 if first speech, 0 otherwise)\\
\addlinespace
body & Statement text\\
fedchamb\_flag & Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)\\
sub1\_flag & Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)\\
sub2\_flag & Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)\\
question & Flag for question (1 if question, 0 otherwise)\\
\addlinespace
answer & Flag for answer (1 if answer, 0 otherwise)\\
q\_in\_writing & Flag for question in writing (1 if question in writing, 0 otherwise)\\
div\_flag & Flag for division (1 if division, 0 otherwise)\\
gender & Gender of speaker\\
uniqueID & Unique identifier of speaker\\
\addlinespace
interject & Flag for interjection (1 if statement is an interjection, 0 otherwise)\\
\bottomrule
\end{tabular}
\end{table}

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. As
well, the \texttt{sub1\_flag} and \texttt{sub2\_flag} variables allow us
to keep track of where various statements are being parsed from in the
XML document. The \texttt{question}, \texttt{answer}, and
\texttt{q\_in\_writing} flags were added to identify statements
belonging to Question Time, and the nature of these statements. We also
flagged for interjections (\texttt{interject}), and the
\texttt{div\_flag} variable was added to flag when a division is called
for. The \texttt{gender} and \texttt{uniqueID} variables were added
based on the main dataset from the \texttt{AustralianPoliticians}
package. Details on the usage of \texttt{uniqueID} will be provided in
Section~\ref{sec-usage}. Further, the \texttt{speech\_no} variable
allows us to keep track of the speech number that each statement and
interjection belongs to. Having the speech number variable offers an
easy way to group statements by speech or isolate specific speeches of
interest. Finally, the \texttt{order} variable was added to maintain the
order of proceedings.

@@

The remaining tests focus on the MPs present on each sitting day. Our
fourth test checks that there is one unique party and electorate
attributed to each individual on each sitting day. As we parsed Hansard
further back in time, we found a number of cases where an individual was
associated with the wrong electorate or party due to transcription
errors. When we found these data errors we corrected them based on the
official release. This test provides us with an automated way to catch
these errors and correct them at scale.

@@

Our sixth test checks that on any given sitting day, the individuals
identified are alive. To do so, we utilized the main dataset from the
\texttt{AustralianPoliticians} package which contains the birth and
where applicable death dates for every politician. This test confirmed
that all MPs who are detected to speak on each sitting day are not
deceased.

Finally, our seventh test validates that all individuals speaking are
MPs on that particular day. We use the \texttt{mps} dataset from the
\texttt{AustralianPoliticians} package which has the dates when each MP
was in parliament. Using these dates, we check that each person speaking
on each sitting day is in fact an MP on that day.

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
Alexander 2019). By including this variable, one can readily integrate
our data records with those available in these two packages.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
Katz, Lindsay, and Rohan Alexander. 2023. {``{A new, comprehensive
database of all proceedings of the Australian Parliamentary Debates
(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7785767}.

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{June 29, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Further, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned. \textbf{Finally, we review the
supplementary Hansard debate topics dataset we created to expand the
versatility of our database.}

@@

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, \textbf{we identified} questions
\textbf{which} were incorrectly transcribed under an answer node and
vice-versa, in which cases we manually corrected the question and answer
flags. For instance, we check for any statements flagged as questions
which include the phrase ``has provided the following answer to the
honourable member's question'', in which case we re-code that statement
as an answer. \textbf{It is important to note, however, that because we
identified and corrected for these transcription errors manually as we
discovered them, additional flagging errors may exist which we did not
catch. As such, users may identify and should be weary of occasional
incorrectly flagged questions or answers in the data.}

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.
\textbf{Despite our best efforts to capture all stage directions in this
list, because it had to be built manually, users should be aware that it
is possible that some stage directions were not separated onto their own
rows in the process. Further, it is important to note that because they
are not spoken aloud, stage directions do not represent speech
components in the same way that all other components such as
interjections and continuations do. However, they provide valuable
information about the inner-workings and structure of parliamentary
events.}

@@

\hypertarget{debate-topics}{%
\subsection{Debate Topics}\label{debate-topics}}

\textbf{To enhance the range of research questions which can be explored
with our data, we have created a supplementary file containing debate
topics and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a time stamp.
Therefore, we took the first available page number child-node for each
debate or sub-debate node to be the one we included in our dataset.}

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022, so there are 1,517 \textbf{individual sitting day} files
for each format. \textbf{Additionally, there is a single corpus file in
both CSV and Parquet forms containing the data from all sitting days,
with a date variable added to allow for distinction and filtering of
individual sitting days. There is also a CSV and Parquet file containing
all parsed debate topics.} All data records are available on the
general-purpose repository Zenodo, at
https://doi.org/10.5281/zenodo.7799678 (Katz and Alexander 2023). For
each \textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{30em}}
\toprule
Variable & Description\\
\midrule
name & Name of speaker\\
order & Individual row numbering, based on our data processing and text separation method\\
speech\_no & Index associated with each speech made on the given sitting day, including all statements, comments and interjections made in the duration of that speech\\
page.no & Page number statement can be found on in official Hansard\\
time.stamp & Time of statement\\
\addlinespace
name.id & Unique member identification code, based on the Parliamentary Handbook\\
electorate & Speaking member's electorate\\
party & Speaking member's party\\
in.gov & Flag for in government (1 if in government, 0 otherwise)\\
first.speech & Flag for first speech (1 if first speech, 0 otherwise)\\
\addlinespace
body & Statement text\\
fedchamb\_flag & Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)\\
question & Flag for question (1 if question, 0 otherwise)\\
answer & Flag for answer (1 if answer, 0 otherwise)\\
q\_in\_writing & Flag for question in writing (1 if question in writing, 0 otherwise)\\
\addlinespace
gender & Gender of speaker\\
uniqueID & Unique identifier of speaker\\
interject & Flag for interjection (1 if statement is an interjection, 0 otherwise)\\
div\_flag & Flag for division (1 if division, 0 otherwise)\\
partyfacts\_id & PartyFacts identification number, based on linked parties data from the Party Facts project\\
\bottomrule
\end{tabular}
\end{table}

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag when a division is called for. The \texttt{gender} and
\texttt{uniqueID} variables were added based on the main dataset from
the \texttt{AustralianPoliticians} package, \textbf{and the
\texttt{partyfacts\_id} variable was added using code and data provided
by the Party Facts Project
\href{https://partyfacts.herokuapp.com}{website}.}\footnote{\textbf{Note
  that in accordance with the code provided on the Party Facts
  {[}downloads page{]}(https://partyfacts.herokuapp.com/download/), we
  used only the core datasets maintained by the Party Facts project,
  which are the Manifesto Project and ParlGov. Details on these datasets
  can be found here:
  https://partyfacts.herokuapp.com/documentation/datasets/.}} Details on
the usage of \texttt{uniqueID} \textbf{and \texttt{partyfacts\_id}} will
be provided in Section~\ref{sec-usage}. Further, the \texttt{speech\_no}
variable allows us to keep track of the speech number that each
statement and interjection belongs to. Having the speech number variable
offers an easy way to group statements by speech or isolate specific
speeches of interest. \textbf{Lastly, the \texttt{order} variable was
added to maintain the order of proceedings, after all individual
statements were separated onto their own rows.}

\textbf{As mentioned, in addition to the Hansard data described above,
our database also contains a CSV and Parquet file with the parsed debate
topics. This file is called \texttt{all\_debate\_topics}, and contains a
\texttt{date} variable specifying the sitting day, an
\texttt{item\_index} variable to specify the order of proceedings
(i.e.~the order in which these topics were discussed), a \texttt{title}
variable containing the debate or sub-debate title contents, and a
\texttt{page.no} variable specifying on which page that title was
recorded to be found in the official Hansard PDF.}

\textbf{Finally, there is a CSV file in our database called
\texttt{PartyFacts\_map.csv}. This file was created using
\texttt{AustralianPoliticians} data, data downloaded from the Party
Facts project, and our own Hansard data \texttt{party} variable. As
there are some party name and abbreviation spelling inconsistencies
across these sources, creating this dataframe allowed us to ensure
correct merging of PartyFacts ID numbers with their associated party, in
accordance with the party abbreviation spelling transcribed in our
Hansard data. Further, we included the corresponding party abbreviation
and full name spelling found in the \texttt{AustralianPoliticians}
package data in this dataframe for completeness.}

\hypertarget{tbl-partyfacts-vars}{}
\begin{table}[H]
\caption{\label{tbl-partyfacts-vars}Summary and description of variables in our Party Facts mapping file }\tabularnewline

\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{25em}}
\toprule
Variable & Description\\
\midrule
partyfacts\_id & PartyFacts identification number, based on linked parties data from the Party Facts project\\
party\_abb\_hansard & Party abbreviation as transcribed in the Hansard data\\
party\_abb\_auspol & Party abbreviation as recorded in the `AustralianPoliticians` data\\
party\_name\_auspol & Party full name as recorded in the `AustralianPoliticians` data\\
\bottomrule
\end{tabular}
\end{table}

@@

\textbf{The fourth test is designed to detect issues in timestamp
formatting in the data, by detecting all time stamps in our database
which do not match the correct ``HH:MM:SS'' format. We found a total of
88 incorrectly formatted time stamps, with common issues such as the
``HH'' or ``MM'' component recorded as ``NaN'' (e.g.~``NaN:28:00'' or
``09:NaN:00''), as well as timestamps with a third digit in the minute
component (e.g.~``09:497:00'' or ``13:445:00''). We took a random sample
of 25\% of these incorrectly formatted timestamps, and manually checked
whether or not they were transcribed as such in the original XML Hansard
transcript. We found that every improperly formatted timestamp in our
random sample was in fact transcribed as such in its original XML file,
meaning these bugs are the result of a transcription error, rather than
an error resulting from our data parsing or cleaning code. As such, we
have left these timestamps in their originally transcribed format in our
database.}

The remaining tests focus on the MPs present on each sitting day. Our
fifth test checks that there is one unique party and electorate
attributed to each individual on each sitting day. As we parsed Hansard
further back in time, we found a number of cases where an individual was
associated with the wrong electorate or party due to transcription
errors. When we found these data errors we corrected them based on the
official release. This test provides us with an automated way to catch
these errors and correct them at scale.

@@

Our seventh test checks that on any given sitting day, the individuals
identified are alive. To do so, we utilized the main dataset from the
\texttt{AustralianPoliticians} package which contains the birth and
where applicable death dates for every politician. This test confirmed
that all MPs who are detected to speak on each sitting day are not
deceased.

Finally, our eighth test validates that all individuals speaking are MPs
on that particular day. We use the \texttt{mps} dataset from the
\texttt{AustralianPoliticians} package which has the dates when each MP
was in parliament. Using these dates, we check that each person speaking
on each sitting day is in fact an MP on that day.

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
Alexander 2019). By including this variable, one can readily integrate
our data records with those available in these two packages.
\textbf{Similarly, we added the \texttt{partyfacts\_id} variable to our
data which allows users to link our data to external political party
information.}

@@

\textbf{Finally, the README file on our GitHub repository and on Zenodo
contains example code on how to read in a file from our database, for
both CSV and Parquet formats. Should a user wish to use the single
Hansard corpus rather than individual sitting day files, we provide
example code on how to read it in, filter for those sitting days of
interest, and split them into distinct data frames. We have also added
example code for filtering out stage directions, and updating the
\texttt{order} variable to reflect the ordering of remaining rows,
should the user wish to remove stage directions from their analysis.
Lastly, the README contains example code showing users how to merge the
debate topics data with a Hansard data file for one sitting day.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
Katz, Lindsay, and Rohan Alexander. 2023. {``{A new, comprehensive
database of all proceedings of the Australian Parliamentary Debates
(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7799678}.
